\documentclass{res}

\usepackage{enumitem}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\setlength{\textheight}{9.5in} % increase text height to fit on 1-page

\begin{document}

% Center the name over the entire width of resume:
\moveleft.5\hoffset\centerline{\large\bf David I. Lovi}
% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
\moveleft.5\hoffset\centerline{Fill In Address Line 1 NW}
\moveleft.5\hoffset\centerline{Edmonton, Alberta T5T XXX}
\moveleft.5\hoffset\centerline{(780) 999-9999}
\moveleft.5\hoffset\centerline{email@somewhere.ca}


\begin{resume}

\section{SUMMARY}
    Software engineer with five years of professional experience and a M.Sc. in Computer Vision.  Values correctness and quality.  Leverages intrinsic thoroughness and automated tests to improve code quality and keep defect rates minimal.  Adept at paratrooping productively into unfamiliar codebases.


\section{EXPERIENCE}
    \vspace{-0.1in}
    \begin{tabbing}
    \hspace{5.15in}\= \kill  % set up one tab position
    \textit{Software Engineer, Contract} \> 5/2017-11/2017
    \end{tabbing}\vspace{-22pt}  % suppress blank line after tabbing
    Voronoi Health Analytics\\
    Coquitlam, BC\\
    \vspace{-2.5ex}\begin{itemize}[noitemsep]
    \item Converted an existing MATLAB prototype of research-grade code for CT-scan segmentation into a marketable sold product for researchers.
    \item Developed python-based automated build and test infrastructure to deliver a product with quality.
    \item Created a paradigm for testing and release engineering that the start-up company can leverage when developing future features, fixes, and new products.
    \item Collaborated remotely with the client in British Columbia.
    \end{itemize}

    \vspace{-0.1in}
    \begin{tabbing}
    \hspace{5.15in}\= \kill  % set up one tab position
    \textit{Software Engineer} \> 5/2012-7/2016
    \end{tabbing}\vspace{-22pt}  % suppress blank line after tabbing
    Dell EMC\\
    Edmonton, AB\\
    \vspace{-2.5ex}\begin{itemize}[noitemsep]
    \item Contributed to both architecture and development for the storage-virtualization product VPLEX in the following broad areas:
    \begin{itemize}[noitemsep]
    \item High availability of the compute systems servicing the I/O path.
    \item Next-generation management-path UI design to improve performance.
    \item Non-disruptive hardware upgrade procedures.
    \end{itemize}
    \item Worked in distributed SCRUM teams with members spanning across Canada, India, and the United States.
    \item Gained experience working with the VMware vSphere API and related technologies as well.  (\textit{E.g.} VMware HA, VMware DRS).
    \end{itemize}

    \vspace{-0.1in}
    \begin{tabbing}
    \hspace{5.15in}\= \kill  % set up one tab position
    \textit{Software Developer, Full-Time \(Summer\)} \> 6/2006-8/2006
    \end{tabbing}\vspace{-22pt}  % suppress blank line after tabbing
    Misericordia Hospital: COMPRU (now iRSM)\\
    Edmonton, AB\\
    \vspace{-2.5ex}\begin{itemize}[noitemsep]
    \item Worked in a team to develop a user-friendly system for patient and appointment management.
    \item The system provided visualization and UI with patient anatomy, \textit{e.g.} for marking and keeping track of areas in the mouth where surgery was performed.
    \item Technologies used: Visual Studio 2005, C\#, SQL Server.
    \end{itemize}


\section{EDUCATION}
    \textit{M.Sc., Computer Science}, September 2011\\
    University of Alberta\\
    \hspace*{2.5em} Thesis: {\textit Incremental Free-Space Carving for Real-Time 3D Reconstruction}\\
    \hspace*{2.5em} Supervisor: Prof. Martin J{\"a}gersand\\
    \hspace*{2.5em} GPA: 3.8/4.0

    \textit{B.Sc., Computer Science}, June 2007\\
    University of Alberta\\
    \hspace*{2.5em} GPA: 3.84/4.0


\section{AWARDS}
    Queen Elizabeth II Graduate Scholarship (Master's), 2008\\
    Amdahl Academic Achievement Scholarship in Computing Science, 2006\\
    Barry J Mailloux Prize in Computing Science, 2005\\
    Terrence Holowach Memorial Prize, 2004\\
    University of Alberta Academic Excellence Scholarship, 2003


\section{RESEARCH}
    \textbf{Publications}\vspace*{0.666ex}
    \begin{itemize}[label={}, labelsep=*, leftmargin=2.8em]
        \item D. Lovi, N. Birkbeck, Hernandez-Herdocia A., A. Rachmielowski, M. J{\"a}gersand, and D. \hspace*{1.5em}Cobzas.  \textit{Predictive Display for Mobile Manipulators in Unknown Environments Using \hspace*{1.5em}Online Vision-Based Monocular Modeling and Localization}. In \textit{IROS}, 2010.
        \item D. Lovi, N. Birkbeck, D. Cobzas, and M. J{\"a}gersand. \textit{Incremental Free-Space Carving for \hspace*{1.5em}Real-Time 3D Reconstruction}. In \textit{3DPVT}, 2010.
    \end{itemize}
    \textbf{External Reviewer}
    \begin{itemize}[label={}, labelsep=*, leftmargin=2.8em]
    \item IEEE/RSJ IROS 2010, IEEE CVPR 2010, IEEE/RSJ IROS 2009, CRV 2009.
    \end{itemize}


\section{SKILLS}
    \textbf{Languages}\\
    \begin{tabular}{ l L{5.5in} }
    \hspace*{1.2em} & C, C++, C\#, Visual Basic, Matlab, LaTeX, HTML. \\
    \end{tabular}

    \textbf{Operating Systems}\\
    \begin{tabular}{ l L{5.5in} }
    \hspace*{1.2em} & Windows, Linux.  Administered Fedora Linux for my M.Sc. supervisor's research laboratory.\\
    \end{tabular}

    \textbf{Academic Focus}\vspace{0.5ex}\\
    \begin{tabular}{ l L{5.5in} }
    \hspace*{1.2em} & Computer vision and graphics, numerical computing and optimization, machine learning.  Thesis research was on real-time computation of 3D scene models from video imagery.  Wrote matrix and linear algebra libraries in C++ using BLAS and LAPACK.  Graduate course projects include automatic face detection using machine learning algorithms as well as reconstruction of 3D architectural scene models from photographs.\\
    \end{tabular}

    \textbf{Miscellaneous}\vspace{0.5ex}\\
    \begin{tabular}{ l L{5.5in} }
    \hspace*{1.2em} & Strong debugging skills and attention to detail.  Communication skills have matured through frequently presenting M.Sc. work in written and oral forms.\\
    \end{tabular}



\end{resume}
\end{document}
